---
title: "STAT627_GroupProject"
author: "Sebastian Zovoko and Lesley Chapman"
date: "6/18/2021"
output: pdf_document
---
### Survivor TV Show data!


(Data)[https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-01/readme.md]
**Description**
The data this week comes from the survivorR R package by way of Daniel Oehm.

596 episodes. 40 seasons. 1 package!

survivoR is a collection of data sets detailing events across all 40 seasons of the US Survivor, including castaway information, vote history, immunity and reward challenge winners and jury votes.

**Research Questions**
+ classifying whether a contestant won using n = 634 and approximately 4 predictors
+ use the outcome of the success of a season, using a metric such as rating, or number of viewers. This would have n = 40 and also 4+ predictors.


```{r, include=FALSE}
#install.packages("tidytuesdayR")
```

```{r, include=FALSE}
library(tidymodels)
library(tidytuesdayR)
library(tidyverse)
library(survivoR)
library(vip)
```


```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2021-06-01')
tuesdata <- tidytuesdayR::tt_load(2021, week = 23)

summary <- tuesdata$summary
```


```{r}
x <- tuesdata$summary
x2 <- tuesdata$castaways
```

```{r}
head(x)
```


```{r}
x3 <- x %>% right_join(x2, by = c("season_name", "season", "full_name"))
```

+ Shuffle Rows
```{r}
set.seed(1234)
rows <- sample(nrow(x3))
x3 <- x3[rows, ]
```

+ Create Response Column : Winner_Count (winner or not)
```{r}
x4 <- x3 %>%
  mutate(Winner_Count = ifelse(winner == castaway, 1,0))
x4
```

+ Impute Missing Values
+ Categorical : fill in with most frequent value
+ Numerical : fill in with zero
```{r}
x4[, sapply(x4, function(x) !is.numeric(x))] <- apply(x4[, sapply(x4, function(x) !is.numeric(x))], 2, function(x) {x[is.na(x)] <- names(sort(table(x), decreasing = TRUE)[1]); x})

x4[is.na(x4)] = 0
```

```{r}
head(x4)
```


```{r}
set.seed(1234)
x5 <- x4
x5 <- x5 %>% select (-c(city, castaway, location,country))

factorfilt = names(x5)
#x5 <- as.character(unlist(x4[,factorfilt]))

x5[, factorfilt] <- lapply(x5[, factorfilt], as.character)

factornames = c("viewers_premier", "viewers_finale", "viewers_reunion", "viewers_mean", "rank", "age", "day", "order", "total_votes_received", "immunity_idols_won", "Winner_Count","season")

x5[, factornames] <- lapply(x5[, factornames], as.numeric)
x5 <- na.omit(x5)
x5_split <- initial_split(x5) 
x5_train <- training(x5_split) 
x5_test <- testing(x5_split)

x5
```

```{r}
x5_formula <- as.factor(Winner_Count) ~ .
lr_spec <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")
lr_fit <- fit(lr_spec, x5_formula, data = x5_train)

```




```{r}
# augment appends predictions at the end of the df
preds <- augment(lr_fit, new_data = x5_test)
```

```{r}
preds
```


```{r}
preds %>%
  conf_mat(estimate = .pred_class, truth = Winner_Count) %>% 
  autoplot(type = "heatmap")
```

https://rpubs.com/Tarid/tidymodel_5

```{r}

lr_fit %>% 
  collect_metrics()
```


```{r}
rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")

rf_recipe <- 
  recipe(as.factor(Winner_Count) ~ ., data = x5_train) %>% 
  step_rm(season)

rf_workflow <- 
  workflow() %>% 
  add_model(rf_mod) %>% 
  add_recipe(rf_recipe)

rf_mod <- 
  rand_forest(mtry = 8, min_n = 7, trees = 1000) %>% 
  set_engine("ranger", num.threads = cores, importance = "impurity") %>% 
  set_mode("classification")

rf_workflow <- 
  rf_workflow %>%
  update_model(rf_mod)

set.seed(1234)

rf_fit <- 
  last_rf_workflow %>% 
  last_fit(x5_split) 

rf_fit
```
## SVM

```{r}
x5_formula <- as.numeric(Winner_Count) ~ .

svm_spec <- svm_poly(degree = 1, cost = 1/4) %>%
  set_engine("kernlab") %>%
  set_mode("regression")

svm_fit <- workflow() %>%
  add_model(svm_spec) %>%
  add_formula(x5_formula) %>%
  fit(x5_train)

svm_fit %>%
  pull_workflow_fit() %>%
  vip(method = "permute", 
      target = "Winner_Count", 
      metric = "rsquared",
      pred_wrapper = kernlab::predict, train = x5_train) + theme_bw()
```

```{r}

x5_test_ <- x5_test %>% select (-c(Winner_Count))
# augment appends predictions at the end of the df
preds <- augment(svm_fit, new_data = x5_test_)

preds %>%
  conf_mat(estimate = .pred_class, truth = Winner_Count) %>% 
  autoplot(type = "heatmap")
```

