---
title: "STAT627_GroupProject"
author: "Sebastian Zovoko and Lesley Chapman"
date: "6/18/2021"
output: pdf_document
---
### Survivor TV Show data!

**Description**
The data this week comes from the survivorR R package by way of Daniel Oehm.

596 episodes. 40 seasons. 1 package!

survivoR is a collection of data sets detailing events across all 40 seasons of the US Survivor, including castaway information, vote history, immunity and reward challenge winners and jury votes.

**Research Questions**
+ classifying whether a contestant won using n = 634 and approximately 4 predictors
+ use the outcome of the success of a season, using a metric such as rating, or number of viewers. This would have n = 40 and also 4+ predictors.


```{r, include=FALSE}
#install.packages("tidytuesdayR")
```

```{r, include=FALSE}
library(tidymodels)
library(tidytuesdayR)
library(tidyverse)
library(survivoR)
```


```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

tuesdata <- tidytuesdayR::tt_load('2021-06-01')
tuesdata <- tidytuesdayR::tt_load(2021, week = 23)

summary <- tuesdata$summary
```


```{r}
head(summary)
```

